---
output: github_document
references:
- id: meratnia2004spatiotemporal
  title: Spatiotemporal compression techniques for moving point objects
  author: 
  - family: Meratnia
    given: Nirvana
  - family: Rolf
    given: A
  container-title: International Conference on Extending Database Technology
  page: 765--782
  issued: 
    year: 2004
  publisher: Springer
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# TopDownTimeRatio

<!-- badges: start -->
<!-- badges: end -->

The goal of TopDownTimeRatio is to condense sequences of longitudinal GPS data into segments for ease of processing. The method used in this package is as outlined in @meratnia2004spatiotemporal. 

## Installation

When it's released (it isn't yet), you can install the released version of TopDownTimeRatio from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("TopDownTimeRatio")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("daniellemccool/TopDownTimeRatio")
```
## Example

Basic usage requires that your data has at least longitude and latitude coordinates as well as a timestamp. You can provide the names if they differ from lon, lat and timestamp.

Here we generate a single segment

```{r example}
library(TopDownTimeRatio)
df <- data.frame(lon = c(5, 5.01, 5.02, 5.05),
                 lat = c(32.01, 32.04, 32.06, 32.10),
                 timestamp = c(500, 600, 800, 2000))

res <- tdtr(df, n_segs = 1)

print(res)
```


Plot example, initial segment
```{r plot, echo = FALSE}
plot(res$lon, res$lat)
segments(res$seg_start_lon, res$seg_start_lat, res$seg_end_lon, res$seg_end_lat)
```


Plot example, new segment at greatest distance
```{r plot2, echo = FALSE}
res <- tdtr(df, n_segs = 2)
plot(res$lon, res$lat)
segments(res$seg_start_lon, res$seg_start_lat, res$seg_end_lon, res$seg_end_lat)
```

